%---------------------------------------------------
% Nombre: bibliografia.tex  
% 
% Bibliografia
%---------------------------------------------------

\begin{thebibliography}{99}


\bibitem{github}
	\emph{} Repositorio del proyecto. \url{https://github.com/joseangeldiazg/DataScience-Titanic}

\bibitem{kernel}
	\emph{} Kernel en Kaggle con el proyecto. \url{https://www.kaggle.com/joseadiazg02/titanic/titanic-0-82-acc-en-test}

\bibitem{trevor}
	\emph{} Titanic: Getting Started With R \url{http://trevorstephens.com/kaggle-titanic-tutorial/getting-started-with-r/}
	
\bibitem{marcio}
	\emph{} Titanic Study \url{https://www.kaggle.com/gualtieri/titanic/titanic-survivorship-analysis/discussion}

\bibitem{history}
	\emph{} Historia del Titanic \url{https://es.wikipedia.org/wiki/RMS_Titanic}

\bibitem{titanic}
	\emph{} Titanic Dataset \url{https://www.kaggle.com/c/titanic/data}		
	
\bibitem{rstudio}
	\emph{} Rstudio Software \url{https://www.rstudio.com}

\bibitem{kaggle}
	\emph{} Website de Kaggle \url{https://www.kaggle.com}	
	
	
	
\bibitem{over}
	\emph{}Nitesh V. Chawla, Kevin W. Bowyer, Lawrence O. Hall, W. Philip Kegelmeyer. "SMOTE: Synthetic Minority Over-sampling Technique"
	
\bibitem{anova}
	\emph{} Anova Test \url{https://en.wikipedia.org/wiki/Analysis_of_variance}
	
\bibitem{c45} 
	\emph{}JR Quinlan. C4. 5: Programming for machine learning, Morgan Kauffmann, 1993

\bibitem{naive}
	\emph{} P. Domingos, M. Pazzani. On the optimality of the simple Bayesian classifier under zero-one loss. Machine Learning 29 (1997) 103-137.

\bibitem{smo}
	\emph{} J. Platt. Fast Training of Support Vector Machines using Sequential Minimal Optimization. In: B. Schoelkopf, C. Burges, A. Smola (Eds.) Advances in Kernel Methods - Support Vector Learning, 1998, 185-208.
	
\bibitem{mlp}
	\emph{} R. Rojas, J. Feldman. Neural Networks: A Systematic Introduction . Springer-Verlag, Berlin, New-York, 1996.
	
\bibitem{id3}
	\emph{} .R. Quinlan. Induction of Decision Trees. Machine Learning 1 (1986) 81-106.
				
		
\end{thebibliography}
%---------------------------------------------------